JD notes on effects

### 2022-05-25 manuscript/jd_notes.Rmd
Autocommit

>>>>

**Bicko**:

- It seems distinguishing between prediction and effects is a bit hard. How about prediction and prediction effects.
	- Predictions: the central line
	- Prediction (predictor?) effects: the curves which describe our uncertainty around the predictions and can be non-isolated (non-anchored) or isolated (anchored)?
